---
title: "Week 1 Quiz"
author: "Aaron Aziz"
date: "6/8/2020"
output: html_document
---

1)The American Community Survey distributes downloadable data about United States communities. Download the 2006 microdata survey about housing for the state of Idaho using download.file() from here:

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06hid.csv

and load the data into R. The code book, describing the variable names is here:

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FPUMSDataDict06.pdf

How many properties are worth $1,000,000 or more?

```{r}
url <- "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06hid.csv"
download.file(url, "./2006microdata.csv", method = "curl")
dateDownloaded1 <- date()

2006microdata <- read.csv("./2006microdata.csv")
#colnames(2006microdata)
sum(2006microdata$VAL == 24, na.rm = TRUE)
```

2) Use the data you loaded from Question 1. Consider the variable FES in the code book. Which of the "tidy data" principles does this variable violate?

```{r}
head(2006microdata)
```

3) Download the Excel spreadsheet on Natural Gas Aquisition Program here:

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FDATA.gov_NGAP.xlsx

Read rows 18-23 and columns 7-15 into R and assign the result to a variable called dat

What is the value of the code below:

```{r}
url <- "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FDATA.gov_NGAP.xlsx"
download.file(url, "./naturalgasdata.xlsx", method = "curl")
dateDownloaded2 <- date()

library(xlsx)
dat <- read.xlsx("./naturalgasdata.xlsx", sheetIndex = 1, header = TRUE, rowIndex = c(18:23), colIndex = c(7:15))
head(dat, 10)
sum(dat$Zip*dat$Ext,na.rm=T)
```

4) Read the XML data on Baltimore restaurants from here:

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Frestaurants.xml

How many restaurants have zipcode 21231?

```{r}
library(XML)
url <- "http://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Frestaurants.xml"
BmoreFood <- xmlTreeParse(url, useInternal = TRUE)
dateDownloaded3 <- date()
rootNode <- xmlRoot(BmoreFood)
xmlName(rootNode)
zip <- xpathSApply(rootNode, "//zipcode", xmlValue)
zip <- as.numeric(zip)
sum(zip == 21231)
```

5)The American Community Survey distributes downloadable data about United States communities. Download the 2006 microdata survey about housing for the state of Idaho using download.file() from here:

using the fread() command load the data into an R object

The following are ways to calculate the average value of the variable

broken down by sex. Using the data.table package, which will deliver the fastest user time?

```{r}
url <- "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06pid.csv"
download.file(url, "./2006microdata2.csv", method = "curl")
dateDownloaded4 <- date()

library(data.table)
DT <- fread("./2006microdata2.csv")
system.time(DT[,mean(pwgtp15),by=SEX])
```


